Capstone Movielens Report

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report section review: OMR Model.

If we predict all unknown ratings with $\hat{\mu}$, we can obtain *RMSE* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108): 
```{r main-script@L108 }
mu.MSEs <- naive_model_MSEs(mu)
```

@@

::: {.noteblock data-latex=""}

The following custom functions described in [Appendix A: Support Functions], are used in the code snippets above:

  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the *MSE* data visualization.

:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
:::

@@

>>>>

If we predict all unknown ratings with $\hat{\mu}$, we can use the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108)  to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$): 
```{r main-script@L108 }
mu.MSEs <- naive_model_MSEs(mu)
```

::: {.noteblock data-latex=""}
In the code snippet above, we use the user-defined function [naive_model_MSEs](#func.naive_model_MSEs) described in the [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions] / [Data Visualization Functions] section of [Appendix A](#appndx_a).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [Models Training: Support Functions] / [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions] / [Data Visualization Functions] section of [Appendix A](#appndx_a).
:::
